---
title: "qmm final"
author: "Sony kiran"
date: "`r Sys.Date()`"
output: html_document
---


## Factors that define the success of the students

The three conditions we considered in predicting student performance are:

1. Course GPA - The student's GPA for a course

2. Proficiency - Defining a student's level of proficiency in the course.

3. Coursework - How thoroughly the student understands the subject.

## Data Collection
GPAs from students should be easy to acquire for course administrators. Other elements can be gathered by a survey/questionnaire or by displaying hands in class.


# Each group has three students out of 12 students.
```{r}
set.seed(26524)
Data_Of_the_Student <- data.frame(Course_GPA = rnorm(12, mean=0.80, sd=0.1),
                       Proficiency = sample(0:1, size=12, replace=TRUE),
                       Coursework = sample.int(5, size=12, replace=TRUE))
```


```{r}
# Ensuring max GPA of 1 and rounding to two places
library(dplyr)
Data_Of_the_Student <- Data_Of_the_Student %>% mutate(Course_GPA=if_else(Course_GPA > 1, 1, round(Course_GPA, 2)))
```


```{r}
head(Data_Of_the_Student)
```
## Decision Variables

Decision variables are members of groups.A value of $H_[i,j]$ indicates whether a student belongs to the group in which the student is jth.

## Objective Function

It is the objective of this project to maximize the chances of success for each individual group.

Since all of the groups will have equal odds of success, we only need to compute the success rate of one group: $textMAX hspace.2cm Z=q 1 $, where $q i$ represents the success rate of the ith group.

Based on the factors above, we can define the chances of success.For all j students in group i,

let $q_i = /Sigma_j / y_j + f_j + 0.2l_j$, 

where,
$y_j$ is the student's GPA, 

$f_j$ is whether they have similar prior proficiency, and 

$l_j$ is their CourseWork.

As needed, the coefficients can be adjusted.

## Constraints considered for this project
The constraints we have considered for this model are the following:

* All groups should have the same likelihood of success.

* Each group has exactly three members.

* A member must be in exactly one group at a time.
```{r}
library(lpSolveAPI)
Student <- read.lp("Finallp.lp")
solve(Student)
```

```{r}
get.objective(Student)
```

```{r}
get.variables(Student)
```
## Decisions from the Group-1,2,3,4
Below are the decisions for where each student should end up: 

Students belongs to Group 1 - 1,8,10

Students belongs to Group 2 - 2,3,5

Students belongs to Group 3 - 4,7,11  

Students belongs to Group 4 - 6,9,12

```
